%-------------------------
% Resume in Latex
% Author : Shangjie Zhou
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Shangjie Zhou} \\ \vspace{6pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:403148885} {+61 403148885}
    $|$
    \faAt \hspace{.5pt} \href{mailto:zhoujay73@gmail.com}{zhoujay73@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/shangjie-jay-zhou-3439a0199/}{LinkedIn}
\end{center}



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Bukalapak}{Melbourne, Australia}
      {Full-stack Engineer - Trust and Fraud}{Jan 2023 \textbf{--} Present, Full-time}
        \resumeItemListStart
            \resumeItem{Participated in company-wide Cost Optimisation project, cutting down frontend infra cost by 40\% with practices on a variety of tools such as gitlab CI/CD, terraform, akamai(CDN) and Kubernetes.}
            \resumeItem{Gave a 45min company-wide "Buka Tech Talk" about Containerisation,  revealing the insights of Docker's implementation through a range of live demo using Go and Ubuntu.}
            \resumeItem{Implemented users' DTTOT(Suspected Terrorists and Terrorist Organizations) checking on reusable KYC micro-service to help Bukalapak subsidiaries comply with government regulations.}
            \resumeItem{Increased the capacity of bulk-logout-users action from 100 to 50000 each job using Kafka.}
        \resumeItemListEnd
        
    \resumeSubheading
      {Navbit}{Sydney, Australia}
      {Frontend Developer}{Oct 2022 \textbf{--} Feb 2023, Casual}
        \resumeItemListStart
            \resumeItem{Developed a web app with React.js and SVG, which provides a case-management application that also supports SVG annotation on X-ray scan images with geometries such as rulers and circular locators.}
        \resumeItemListEnd

    \resumeSubheading
      {Biyou Technology}{Zhuhai, China}
      {Frontend Developer}{Nov 2021 \textbf{--} Feb 2022, Internship}
        \resumeItemListStart
            \resumeItem{Developed and maintained frontend applications by collaborating with a cross-functional team including UI designers, product managers and other software engineers.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd




%----------- Projects -----------

\section{Projects}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{\href{https://www.npmjs.com/package/simple-annotate-zsj}{Simple Annotator (NPM package):}}{ I published an NPM React component library that allows people to annotate images with SVGs} \\ \vspace{3pt}

        \textbf{\href{https://github.com/ShangjieZhou/my-little-react/tree/main}{My Little React (GitHub Project):}}{ A self-implemented frontend framework that mimics React's basic mechanism of components' state management and interaction with the DOM} \\ \vspace{3pt}

        \textbf{\href{https://dev.to/jayzho/understand-async-in-js-the-core-concepts-1j92}{Async in JS (Dev Blog):}}{ An article that explores the insights of Javascript's async mechanism } \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd


%----------- EDUCATION -----------

\section{Education}
  \vspace{6pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {University of New South Wales (UNSW)}{Sydney, Australia}
      {Bachelor of Engineering(Honours) in Software Engineering}{Feb 2018 \textbf{--} Feb 2023}
      \resumeSubHeadingListStart
        \small{\item{
            \textbf{Honours Class 1:} Graduated with the highest Class of Honours with WAM of at least 80 and thesis course mark of at least 65.}}
        \small{\item{
            \textbf{Dean's Honours List (2021):} For high achieving undergraduate students at UNSW Engineering.}}
        \small{\item{
            \textbf{Thesis - Validation of XML Electronic Invoices:} Built a backend API and a frontend application that dynamically validates UBL invoices against validation rules specified by users. }}
        \small{\item{
            \textbf{Courses:} Data Structures and Algorithms (93), Extended Algorithms and Programming Techniques (91), Computer Graphics (89), Programming Languages and Compilers (95), Computer Networks (93), Operating Systems (88). }}
        \resumeSubHeadingListEnd
    
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Programming Languages:}{ Proficient in Go, SQL, Python, Javascipt, HTML, CSS/SCSS; familiar with Java, C, Haskell, Dart, MIPS.} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Docker, Kubernetes, gRPC, MySQL, Git, Gitlab CI/CD, Linux, React.js, Vue.js, Three.js, SVGs, OpenGL, Flutter, Flask.} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd


%----------- Personal Details -----------


\section{Personal Details}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ English(Full professional proficiency), Mandarin(Native).} \\ \vspace{3pt}
        
        \textbf{Work Rights:}{ Temporary Graduate Visa(Subclass 485), will be valid until Jun 2027.} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd


%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
